Lens Modeling in \sw

### 2014-01-22 text/ms-before.tex

\usepackage{graphicx}
% prefere pdf over png (better quality, lossless compression)
\DeclareGraphicsExtensions{%
  .pdf,.PDF,%
  .png,.PNG,%
  .jpg,.mps,.jpeg,.jbig2,.jb2,.JPG,.JPEG,.JBIG2,.JB2}

@@

\begin{figure}[h]
\centering
\includegraphics[width=.7\hsize]{fig/lenssky}
\caption{Sky distribution of 398 published lenses considered secure as
  of September 2013 (from the Masterlens catalog at the University of
  Utah, maintained by Joel Brownstein and Leonidas Moustakas.) The map
  is in Hammer-Aitoff projection, with North up and $\rm RA=0$ in the
  middle.  The empty swathes to the left and right of center are the
  Milky Way.}
\label{fig:masterlens}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[height=.3\vsize]{fig/arriv1}
\includegraphics[height=.3\vsize]{fig/arriv2}
\includegraphics[height=.3\vsize]{fig/arriv3}
\caption{Arrival-time surfaces, with contour levels of equal arrival
  time.  The upper surface is with no lens.  The middle surface is
  when a circular lensing mass (offset from the source) is added; a
  maximum, a minimum and a saddle point can be seen.  The last surface
  is the result of an elongated lensing mass; a maximum, two minima
  and two saddle points can be seen.
}
\label{fig:arriv}
\end{figure}

@@

\begin{figure}
  \centering
  \subfigure{\includegraphics[width=0.45\textwidth]
             {fig/006941_input}} \\
  \subfigure{\includegraphics[width=0.45\textwidth]
             {fig/007022_input}} \\
  \subfigure{\includegraphics[width=0.45\textwidth]
             {fig/006919_input}}
  \caption{Examples of Spaghetti input.  The models from these appear
    later in Figures \ref{fig:6941}, \ref{fig:7022} and \ref{fig:6919}.
  }
  \label{fig:input-spag}
\end{figure}

@@

\begin{figure}
  \centering
  \subfigure[real mass distribution]{
    \label{fig:6941_sim_mass}
    \includegraphics[width=0.45\textwidth]{fig/ASW000102p_kappa}
  }
  \subfigure[real arrival-time surface]{
    \label{fig:6941_sim_arr}
    \includegraphics[width=0.45\textwidth]{fig/ASW000102p_arriv}
  }
  \subfigure[model mass distribution]{
    \label{fig:6941_mass}
    \includegraphics[width=0.45\textwidth]{fig/006941_mass}
  }
  \subfigure[model arrival-time surface]{
    \label{fig:6941_cont}
    \includegraphics[width=0.45\textwidth]{fig/006941_spaghetti}
  }
  \subfigure[real vs model enclosed mass]{
    \label{fig:6941_kappa}
    \includegraphics[width=0.45\textwidth]{fig/006941_kappa_encl}
  }
  \subfigure[model lensed image]{
    \label{fig:6941_atime}
    \includegraphics[width=0.45\textwidth]{fig/006941_arr_time}
  }
  \caption[result 6941 (ASW000102p)]{Sim ASW000102p and a model.  A
    simple configuration; the model input is shown in the top panel of
    Figure~\ref{fig:input-spag}.  For details of the individual panels
    here, see section \ref{sec:example_models}.}
  \label{fig:6941}
\end{figure}

\begin{figure}
  \centering
  \subfigure[real mass distribution]{
    \label{fig:6975_sim_mass}
    \includegraphics[width=0.45\textwidth]{fig/ASW000195x_kappa}
  }
  \subfigure[real arrival-time surface]{
    \label{fig:6975_sim_arr}
    \includegraphics[width=0.45\textwidth]{fig/ASW000195x_arriv}
  }
  \subfigure[model mass distribution]{
    \label{fig:6975_mass}
    \includegraphics[width=0.45\textwidth]{fig/006975_mass}
  }
  \subfigure[model arrival-time surface]{
    \label{fig:6975_cont}
    \includegraphics[width=0.45\textwidth]{fig/006975_spaghetti}
  }
  \subfigure[real vs model enclosed mass]{
    \label{fig:6975_kappa}
    \includegraphics[width=0.45\textwidth]{fig/006975_kappa_encl}
  }
  \subfigure[model lensed image]{
    \label{fig:6975_atime}
    \includegraphics[width=0.45\textwidth]{fig/006975_arr_time}
  }
  \caption[result 6975 (ASW000195x)]{Sim ASW000195x and a
    model.}
  \label{fig:6975}
\end{figure}

\begin{figure}
  \centering
  \subfigure[real mass distribution]{
    \label{fig:6937_sim_mass}
    \includegraphics[width=0.45\textwidth]{fig/ASW0000vqg_kappa}
  }
  \subfigure[real arrival-time surface]{
    \label{fig:6937_sim_arr}
    \includegraphics[width=0.45\textwidth]{fig/ASW0000vqg_arriv}
  }
  \subfigure[model mass distribution]{
    \label{fig:6937_mass}
    \includegraphics[width=0.45\textwidth]{fig/006937_mass}
  }
  \subfigure[model arrival-time surface]{
    \label{fig:6937_cont}
    \includegraphics[width=0.45\textwidth]{fig/006937_spaghetti}
  }
  \subfigure[real vs model enclosed mass]{
    \label{fig:6937_kappa}
    \includegraphics[width=0.45\textwidth]{fig/006937_kappa_encl}
  }
  \subfigure[model lensed image]{
    \label{fig:6937_atime}
    \includegraphics[width=0.45\textwidth]{fig/006937_arr_time}
  }
  \caption[result 6937 (ASW0000vqg)]{Sim ASW0000vqg and a model.}
  \label{fig:6937}
\end{figure}

\begin{figure}
  \centering
  \subfigure[real mass distribution]{
    \label{fig:6990_sim_mass}
    \includegraphics[width=0.45\textwidth]{fig/ASW0004oux_kappa}
  }
  \subfigure[real arrival-time surface]{
    \label{fig:6990_sim_arr}
    \includegraphics[width=0.45\textwidth]{fig/ASW0004oux_arriv}
  }
  \subfigure[model mass distribution]{
    \label{fig:6990_mass}
    \includegraphics[width=0.45\textwidth]{fig/006990_mass}
  }
  \subfigure[model arrival-time surface]{
    \label{fig:6990_cont}
    \includegraphics[width=0.45\textwidth]{fig/006990_spaghetti}
  }
  \subfigure[real vs model enclosed mass]{
    \label{fig:6990_kappa}
    \includegraphics[width=0.45\textwidth]{fig/006990_kappa_encl}
  }
  \subfigure[model lensed image]{
    \label{fig:6990_atime}
    \includegraphics[width=0.45\textwidth]{fig/006990_arr_time}
  }

@@

\begin{figure}
  \centering
  \subfigure[real mass distribution]{
    \label{fig:6915_sim_mass}
    \includegraphics[width=0.45\textwidth]{fig/ASW0001hpf_kappa}
  }
  \subfigure[real arrival-time surface]{
    \label{fig:6915_sim_arr}
    \includegraphics[width=0.45\textwidth]{fig/ASW0001hpf_arriv}
  }
  \subfigure[model mass distribution]{
    \label{fig:6915_mass}
    \includegraphics[width=0.45\textwidth]{fig/006915_mass}
  }
  \subfigure[model arrival-time surface]{
    \label{fig:6915_cont}
    \includegraphics[width=0.45\textwidth]{fig/006915_spaghetti}
  }
  \subfigure[real vs model enclosed mass]{
    \label{fig:6915_kappa}
    \includegraphics[width=0.45\textwidth]{fig/006915_kappa_encl}
  }
  \subfigure[model lensed image]{
    \label{fig:6915_atime}
    \includegraphics[width=0.45\textwidth]{fig/006915_arr_time}
  }

@@

\begin{figure}
  \centering
  \subfigure[real mass distribution]{
    \label{fig:7022_sim_mass}
    \includegraphics[width=0.45\textwidth]{fig/ASW0000h2m_kappa}
  }
  \subfigure[real arrival-time surface]{
    \label{fig:7022_sim_arr}
    \includegraphics[width=0.45\textwidth]{fig/ASW0000h2m_arriv}
  }
  \subfigure[model mass distribution]{
    \label{fig:7022_mass}
    \includegraphics[width=0.45\textwidth]{fig/007022_mass}
  }
  \subfigure[model arrival-time surface]{
    \label{fig:7022_cont}
    \includegraphics[width=0.45\textwidth]{fig/007022_spaghetti}
  }
  \subfigure[real vs model enclosed mass]{
    \label{fig:7022_kappa}
    \includegraphics[width=0.45\textwidth]{fig/007022_kappa_encl}
  }
  \subfigure[model lensed image]{
    \label{fig:7022_atime}
    \includegraphics[width=0.45\textwidth]{fig/007022_arr_time}
  }

@@

\begin{figure}
  \centering
  \subfigure[real mass distribution]{
    \label{fig:7025_sim_mass}
    \includegraphics[width=0.45\textwidth]{fig/ASW0000h2m_kappa}
  }
  \subfigure[real arrival-time surface]{
    \label{fig:7025_sim_arr}
    \includegraphics[width=0.45\textwidth]{fig/ASW0000h2m_arriv}
  }
  \subfigure[model mass distribution]{
    \label{fig:7025_mass}
    \includegraphics[width=0.45\textwidth]{fig/007025_mass}
  }
  \subfigure[model arrival-time surface]{
    \label{fig:7025_cont}
    \includegraphics[width=0.45\textwidth]{fig/007025_spaghetti}
  }
  \subfigure[real vs model enclosed mass]{
    \label{fig:7025_kappa}
    \includegraphics[width=0.45\textwidth]{fig/007025_kappa_encl}
  }
  \subfigure[model lensed image]{
    \label{fig:7025_atime}
    \includegraphics[width=0.45\textwidth]{fig/007025_arr_time}
  }

@@

\begin{figure}
  \centering
  \subfigure[real mass distribution]{
    \label{fig:6919_sim_mass}
    \includegraphics[width=0.45\textwidth]{fig/ASW0002z6f_kappa}
  }
  \subfigure[real arrival-time surface]{
    \label{fig:6919_sim_arr}
    \includegraphics[width=0.45\textwidth]{fig/ASW0002z6f_arriv}
  }
  \subfigure[model mass distribution]{
    \label{fig:6919_mass}
    \includegraphics[width=0.45\textwidth]{fig/006919_mass}
  }
  \subfigure[model arrival-time surface]{
    \label{fig:6919_cont}
    \includegraphics[width=0.45\textwidth]{fig/006919_spaghetti}
  }
  \subfigure[real vs model enclosed mass]{
    \label{fig:6919_kappa}
    \includegraphics[width=0.45\textwidth]{fig/006919_kappa_encl}
  }
  \subfigure[model lensed image]{
    \label{fig:6919_atime}
    \includegraphics[width=0.45\textwidth]{fig/006919_arr_time}
  }
  \caption[result 6919 (ASW0002z6f)]{Sim ASW0002z6f and a model.  The
    model input appears in the bottom panel of Figure
    \ref{fig:input-spag}. An incipient quad}
  \label{fig:6919}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
    \includegraphics[width=0.80\textwidth]{fig/eR_4}
  \caption{Relative \ERf / \ERg[, sim] for models by volunteers (blue cross), models made by an expert (red cross with offset), including rejected models (green squares); binned per sim.}
  \label{fig:ER_per_sim}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
    \includegraphics[width=0.80\textwidth]{fig/eR_1}
  \caption{\ERf for all models with estimated errors in blue squares, \ERg of simulation in red crosses}
  \label{fig:ER_all_models}
\end{figure}

>>>>

@@

\begin{figure}
\centering
\includegraphics[width=.8\hsize]{fig/lenssky.png}
\caption{Sky distribution of 398 published lenses considered secure as
  of September 2013 (from the Masterlens catalog at the University of
  Utah, maintained by Joel Brownstein and Leonidas Moustakas.) The map
  is in Hammer-Aitoff projection, with North up and $\rm RA=0$ in the
  middle.  The empty swathes to the left and right of center are the
  Milky Way.}
\label{fig:masterlens}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[height=.3\vsize]{fig/arriv1.png}
\includegraphics[height=.3\vsize]{fig/arriv2.png}
\includegraphics[height=.3\vsize]{fig/arriv3.png}
\caption{Arrival-time surfaces, with contour levels of equal arrival
  time.  The upper surface is with no lens.  The middle surface is
  when a circular lensing mass (offset from the source) is added; a
  maximum, a minimum and a saddle point can be seen.  The last surface
  is the result of an elongated lensing mass; a maximum, two minima
  and two saddle points can be seen.
}
\label{fig:arriv}
\end{figure}

@@

\begin{figure}
  \centering
  \subfigure{\includegraphics[width=0.45\textwidth]
             {fig/006941_input.png}} \\
  \subfigure{\includegraphics[width=0.45\textwidth]
             {fig/007022_input.png}} \\
  \subfigure{\includegraphics[width=0.45\textwidth]
             {fig/006919_input.png}}
  \caption{Examples of Spaghetti input.  The models from these appear
    later in Figures \ref{fig:6941}, \ref{fig:7022} and \ref{fig:6919}.
  }
  \label{fig:input-spag}
\end{figure}

@@

\begin{figure}
  \centering
  \subfigure[real mass distribution]{
    \label{fig:6941_sim_mass}
    \includegraphics[width=0.45\textwidth]{fig/ASW000102p_kappa.png}
  }
  \subfigure[real arrival-time surface]{
    \label{fig:6941_sim_arr}
    \includegraphics[width=0.45\textwidth]{fig/ASW000102p_arriv.png}
  }
  \subfigure[model mass distribution]{
    \label{fig:6941_mass}
    \includegraphics[width=0.45\textwidth]{fig/006941_mass.png}
  }
  \subfigure[model arrival-time surface]{
    \label{fig:6941_cont}
    \includegraphics[width=0.45\textwidth]{fig/006941_spaghetti.png}
  }
  \subfigure[real vs model enclosed mass]{
    \label{fig:6941_kappa}
    \includegraphics[width=0.45\textwidth]{fig/006941_kappa_encl.png}
  }
  \subfigure[model lensed image]{
    \label{fig:6941_atime}
    \includegraphics[width=0.45\textwidth]{fig/006941_arr_time.png}
  }
  \caption[result 6941 (ASW000102p)]{Sim ASW000102p and a model.  A
    simple configuration; the model input is shown in the top panel of
    Figure~\ref{fig:input-spag}.  For details of the individual panels
    here, see section \ref{sec:example_models}.}
  \label{fig:6941}
\end{figure}

\begin{figure}
  \centering
  \subfigure[real mass distribution]{
    \label{fig:6975_sim_mass}
    \includegraphics[width=0.45\textwidth]{fig/ASW000195x_kappa.png}
  }
  \subfigure[real arrival-time surface]{
    \label{fig:6975_sim_arr}
    \includegraphics[width=0.45\textwidth]{fig/ASW000195x_arriv.png}
  }
  \subfigure[model mass distribution]{
    \label{fig:6975_mass}
    \includegraphics[width=0.45\textwidth]{fig/006975_mass.png}
  }
  \subfigure[model arrival-time surface]{
    \label{fig:6975_cont}
    \includegraphics[width=0.45\textwidth]{fig/006975_spaghetti.png}
  }
  \subfigure[real vs model enclosed mass]{
    \label{fig:6975_kappa}
    \includegraphics[width=0.45\textwidth]{fig/006975_kappa_encl.png}
  }
  \subfigure[model lensed image]{
    \label{fig:6975_atime}
    \includegraphics[width=0.45\textwidth]{fig/006975_arr_time.png}
  }
  \caption[result 6975 (ASW000195x)]{Sim ASW000195x and a
    model.}
  \label{fig:6975}
\end{figure}

\begin{figure}
  \centering
  \subfigure[real mass distribution]{
    \label{fig:6937_sim_mass}
    \includegraphics[width=0.45\textwidth]{fig/ASW0000vqg_kappa.png}
  }
  \subfigure[real arrival-time surface]{
    \label{fig:6937_sim_arr}
    \includegraphics[width=0.45\textwidth]{fig/ASW0000vqg_arriv.png}
  }
  \subfigure[model mass distribution]{
    \label{fig:6937_mass}
    \includegraphics[width=0.45\textwidth]{fig/006937_mass.png}
  }
  \subfigure[model arrival-time surface]{
    \label{fig:6937_cont}
    \includegraphics[width=0.45\textwidth]{fig/006937_spaghetti.png}
  }
  \subfigure[real vs model enclosed mass]{
    \label{fig:6937_kappa}
    \includegraphics[width=0.45\textwidth]{fig/006937_kappa_encl.png}
  }
  \subfigure[model lensed image]{
    \label{fig:6937_atime}
    \includegraphics[width=0.45\textwidth]{fig/006937_arr_time.png}
  }
  \caption[result 6937 (ASW0000vqg)]{Sim ASW0000vqg and a model.}
  \label{fig:6937}
\end{figure}

\begin{figure}
  \centering
  \subfigure[real mass distribution]{
    \label{fig:6990_sim_mass}
    \includegraphics[width=0.45\textwidth]{fig/ASW0004oux_kappa.png}
  }
  \subfigure[real arrival-time surface]{
    \label{fig:6990_sim_arr}
    \includegraphics[width=0.45\textwidth]{fig/ASW0004oux_arriv.png}
  }
  \subfigure[model mass distribution]{
    \label{fig:6990_mass}
    \includegraphics[width=0.45\textwidth]{fig/006990_mass.png}
  }
  \subfigure[model arrival-time surface]{
    \label{fig:6990_cont}
    \includegraphics[width=0.45\textwidth]{fig/006990_spaghetti.png}
  }
  \subfigure[real vs model enclosed mass]{
    \label{fig:6990_kappa}
    \includegraphics[width=0.45\textwidth]{fig/006990_kappa_encl.png}
  }
  \subfigure[model lensed image]{
    \label{fig:6990_atime}
    \includegraphics[width=0.45\textwidth]{fig/006990_arr_time.png}
  }

@@

\begin{figure}
  \centering
  \subfigure[real mass distribution]{
    \label{fig:6915_sim_mass}
    \includegraphics[width=0.45\textwidth]{fig/ASW0001hpf_kappa.png}
  }
  \subfigure[real arrival-time surface]{
    \label{fig:6915_sim_arr}
    \includegraphics[width=0.45\textwidth]{fig/ASW0001hpf_arriv.png}
  }
  \subfigure[model mass distribution]{
    \label{fig:6915_mass}
    \includegraphics[width=0.45\textwidth]{fig/006915_mass.png}
  }
  \subfigure[model arrival-time surface]{
    \label{fig:6915_cont}
    \includegraphics[width=0.45\textwidth]{fig/006915_spaghetti.png}
  }
  \subfigure[real vs model enclosed mass]{
    \label{fig:6915_kappa}
    \includegraphics[width=0.45\textwidth]{fig/006915_kappa_encl.png}
  }
  \subfigure[model lensed image]{
    \label{fig:6915_atime}
    \includegraphics[width=0.45\textwidth]{fig/006915_arr_time.png}
  }

@@

\begin{figure}
  \centering
  \subfigure[real mass distribution]{
    \label{fig:7022_sim_mass}
    \includegraphics[width=0.45\textwidth]{fig/ASW0000h2m_kappa.png}
  }
  \subfigure[real arrival-time surface]{
    \label{fig:7022_sim_arr}
    \includegraphics[width=0.45\textwidth]{fig/ASW0000h2m_arriv.png}
  }
  \subfigure[model mass distribution]{
    \label{fig:7022_mass}
    \includegraphics[width=0.45\textwidth]{fig/007022_mass.png}
  }
  \subfigure[model arrival-time surface]{
    \label{fig:7022_cont}
    \includegraphics[width=0.45\textwidth]{fig/007022_spaghetti.png}
  }
  \subfigure[real vs model enclosed mass]{
    \label{fig:7022_kappa}
    \includegraphics[width=0.45\textwidth]{fig/007022_kappa_encl.png}
  }
  \subfigure[model lensed image]{
    \label{fig:7022_atime}
    \includegraphics[width=0.45\textwidth]{fig/007022_arr_time.png}
  }

@@

\begin{figure}
  \centering
  \subfigure[real mass distribution]{
    \label{fig:7025_sim_mass}
    \includegraphics[width=0.45\textwidth]{fig/ASW0000h2m_kappa.png}
  }
  \subfigure[real arrival-time surface]{
    \label{fig:7025_sim_arr}
    \includegraphics[width=0.45\textwidth]{fig/ASW0000h2m_arriv.png}
  }
  \subfigure[model mass distribution]{
    \label{fig:7025_mass}
    \includegraphics[width=0.45\textwidth]{fig/007025_mass.png}
  }
  \subfigure[model arrival-time surface]{
    \label{fig:7025_cont}
    \includegraphics[width=0.45\textwidth]{fig/007025_spaghetti.png}
  }
  \subfigure[real vs model enclosed mass]{
    \label{fig:7025_kappa}
    \includegraphics[width=0.45\textwidth]{fig/007025_kappa_encl.png}
  }
  \subfigure[model lensed image]{
    \label{fig:7025_atime}
    \includegraphics[width=0.45\textwidth]{fig/007025_arr_time.png}
  }

@@

\begin{figure}
  \centering
  \subfigure[real mass distribution]{
    \label{fig:6919_sim_mass}
    \includegraphics[width=0.45\textwidth]{fig/ASW0002z6f_kappa.png}
  }
  \subfigure[real arrival-time surface]{
    \label{fig:6919_sim_arr}
    \includegraphics[width=0.45\textwidth]{fig/ASW0002z6f_arriv.png}
  }
  \subfigure[model mass distribution]{
    \label{fig:6919_mass}
    \includegraphics[width=0.45\textwidth]{fig/006919_mass.png}
  }
  \subfigure[model arrival-time surface]{
    \label{fig:6919_cont}
    \includegraphics[width=0.45\textwidth]{fig/006919_spaghetti.png}
  }
  \subfigure[real vs model enclosed mass]{
    \label{fig:6919_kappa}
    \includegraphics[width=0.45\textwidth]{fig/006919_kappa_encl.png}
  }
  \subfigure[model lensed image]{
    \label{fig:6919_atime}
    \includegraphics[width=0.45\textwidth]{fig/006919_arr_time.png}
  }
  \caption[result 6919 (ASW0002z6f)]{Sim ASW0002z6f and a model.  The
    model input appears in the bottom panel of Figure
    \ref{fig:input-spag}. An incipient quad}
  \label{fig:6919}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
    \includegraphics[width=0.80\textwidth]{fig/eR_4.png}
  \caption{Relative \ERf / \ERg[, sim] for models by volunteers (blue cross), models made by an expert (red cross with offset), including rejected models (green squares); binned per sim.}
  \label{fig:ER_per_sim}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
    \includegraphics[width=0.80\textwidth]{fig/eR_1.png}
  \caption{\ERf for all models with estimated errors in blue squares, \ERg of simulation in red crosses}
  \label{fig:ER_all_models}
\end{figure}

### 2014-01-22 text/ms.tex

\begin{abstract}
In the initial phase of \sw (SW1), volunteers were invited to search the CFHTLS sky survey to look for gravitational lenses.
Here we report on a web application that gives experienced volunteers the opportunity to model the candidates that have been identified.
These volunteers were also invited to model a sample of 29 simulated lenses in order to gauge the quality of the models that were being generated.
These were then examined in greater detail, with particular attention being paid to the following:
(i)~identification of image parities and time arrivals;
(ii)~the mean convergence (equivalent to the enclosed mass), and finally;
(iii)~the performance of a volunteer vs. a professional.
In most cases, the volunteers were found to correctly identify the image parities and time arrivals, along with a mean convergence that was contained within the image region.
In all, the results could be comparable to that of professionals.

>>>>

\begin{abstract}
In the initial phase of \sw (SW1), volunteers were invited to search the CFHTLS sky survey to look for gravitational lenses.
Here we report on a web application that gives experienced volunteers the opportunity to model the candidates that have been identified.
These volunteers were also invited to model a sample of 29 simulated lenses in order to gauge the quality of the models that were being generated.
These were then examined in greater detail, with particular attention being paid to the following:
(i)~identification of image parities and time arrivals;
(ii)~the mean convergence (equivalent to the enclosed mass), and finally;
(iii)~the performance of a volunteer vs. a professional.
In most cases, the volunteers were found to correctly identify the image parities and time arrivals.
% Einstein radius +~20%
 along with a mean convergence that was contained within the image region.
In all, the results could be comparable to that of professionals.
